ABM simulating short-term mating behaviors

### 2022-05-16 submission/manuscript.Rmd
minor edits to the figures

---
output:
  pdf_document:
    keep_tex: true
geometry: margin=1.0in
fontsize: 11pt
numbersections: true
bibliography: reference.bib
csl: evolution-and-human-behavior.csl
header-includes:
  - \newcommand{\bcenter}{\begin{center}}
  - \newcommand{\ecenter}{\end{center}}
  - \newcommand{\btitlepage}{\begin{titlepage}}
  - \newcommand{\etitlepage}{\end{titlepage}}
  - \usepackage{setspace}\doublespacing
  - \usepackage{helvet}
  - \renewcommand*\familydefault{\sfdefault}
  - \usepackage{booktabs}
  - \usepackage[font=small,labelfont=bf]{caption}
---

@@

# An Agent-based Model of Gender Differences in Short-term Mating Behaviors as a Result of Mating Preferences {-}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=70mm]{figures/fig1_men_vs_women.pdf}
  \caption{\textbf{Short-term mating behaviors of men and women after 1,000 time steps in the model when gender differences existed in mating preferences.} Violin plots summarizing the outcome variables separately for heterosexual individuals and gay men and lesbian women. Plot (A) shows the average number of short-term mating experiences, and plot (B) shows the average number of short-term mates. Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar. Statistics were calculated using the full population of men and women in the model (\textit{N\textsubscript{m}} = \textit{N\textsubscript{w}} = 150).}
\end{figure}

>>>>

---
output:
  pdf_document:
    keep_tex: true
  word_document: true
geometry: margin=1.0in
fontsize: 11pt
numbersections: true
bibliography: reference.bib
csl: evolution-and-human-behavior.csl
header-includes:
  - \newcommand{\bcenter}{\begin{center}}
  - \newcommand{\ecenter}{\end{center}}
  - \newcommand{\btitlepage}{\begin{titlepage}}
  - \newcommand{\etitlepage}{\end{titlepage}}
  - \usepackage{setspace}\doublespacing
  - \usepackage{helvet}
  - \renewcommand*\familydefault{\sfdefault}
  - \usepackage{booktabs}
  - \usepackage[font=small,labelfont=bf]{caption}
---

@@

# An Agent-Based Model of Gender Differences in Short-Term Mating Behaviors as a Result of Mating Preferences {-}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=100mm]{figures/fig1_men_vs_women.pdf}
  \caption{\textbf{Short-term mating behaviors of men and women after 1,000 time steps in the model when gender differences existed in mating preferences.} Violin plots summarizing the outcome variables separately for heterosexual individuals and gay men and lesbian women. Plot (A) shows the average number of short-term mating experiences, and plot (B) shows the average number of short-term mates. Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar. Statistics were calculated using the full population of men and women in the model (\textit{N\textsubscript{m}} = \textit{N\textsubscript{w}} = 150).}
\end{figure}

### 2022-05-16 submission/manuscript.tex
minor edits to the figures

\hypertarget{an-agent-based-model-of-gender-differences-in-short-term-mating-behaviors-as-a-result-of-mating-preferences}{%
\section*{An Agent-based Model of Gender Differences in Short-term
Mating Behaviors as a Result of Mating
Preferences}\label{an-agent-based-model-of-gender-differences-in-short-term-mating-behaviors-as-a-result-of-mating-preferences}}
\addcontentsline{toc}{section}{An Agent-based Model of Gender
Differences in Short-term Mating Behaviors as a Result of Mating
Preferences}

>>>>

\hypertarget{an-agent-based-model-of-gender-differences-in-short-term-mating-behaviors-as-a-result-of-mating-preferences}{%
\section*{An Agent-Based Model of Gender Differences in Short-Term
Mating Behaviors as a Result of Mating
Preferences}\label{an-agent-based-model-of-gender-differences-in-short-term-mating-behaviors-as-a-result-of-mating-preferences}}
\addcontentsline{toc}{section}{An Agent-Based Model of Gender
Differences in Short-Term Mating Behaviors as a Result of Mating
Preferences}
